\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-20 paper/main.tex
added ref

\textcolor{blue}{To quantitatively evaluate the relative predictive performances of the models on the semantic interference data, we used a Bayes factor analysis. We computed Bayes factors for the two-cues model compared to the three-cues model and to the one cue model, respectively. Since Bayes factors are sensitive to the choice of priors on the parameters of interest, we computed Bayes factors under six different priors for the latency factor parameter $F$,
$Normal$(0.01,0.01), 
$Normal$(0.01,0.02),
$Normal$(0.01,0.005),
$Normal$(0.02,0.01),
$Normal$(0.02,0.02), and 
$Normal$(0.02,0.005). }

>>>>

\textcolor{blue}{To quantitatively evaluate the relative predictive performances of the models on the semantic interference data, we used a Bayes factor analysis. We computed Bayes factors for the two-cues model compared to the three-cues model and to the one cue model, respectively. Since Bayes factors are sensitive to the choice of priors on the parameters of interest \citep{kass1995bayes}, we computed Bayes factors under six different priors for the latency factor parameter $F$,
$Normal$(0.01,0.01), 
$Normal$(0.01,0.02),
$Normal$(0.01,0.005),
$Normal$(0.02,0.01),
$Normal$(0.02,0.02), and 
$Normal$(0.02,0.005).}
